%-------------------------
% Resume in LaTeX
% Author: Hamza Khan
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tight margins for one page
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{navy}{HTML}{1B3A6B}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\color{navy}
}{}{0em}{}[\color{navy}\titlerule\vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1\vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{1pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
  {\LARGE\scshape\color{navy} Hamza Khan} \\[3pt]
  \small
  +92-347-8479617 $|$
  \href{mailto:muhammadhamzakhanmarwat@gmail.com}{\underline{muhammadhamzakhanmarwat@gmail.com}} $|$
  \href{https://linkedin.com/in/muhammad-hamza-khan-4ab661297}{\underline{linkedin.com/in/muhammad-hamza-khan}} $|$
  \href{https://github.com/Hamzachan69}{\underline{github.com/Hamzachan69}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {FAST NUCES}{Peshawar}
    {Bachelor of Science in Computer Science}{Aug 2022 -- Present}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Junior Unity Game Developer}{Nov 2024 -- July 2025}
    {Cognitive Force (Remote) · Lahore}{}
    \resumeItemListStart
      \resumeItem{Redesigned the full interface of the \textbf{Origami Configurator} app and ported it to a browser-based version, keeping all features intact --- 3D model viewing, product setup, pricing, and core construction tools.}
      \resumeItem{Reduced app size for fast loading across devices without installation, and improved internal stability and performance.}
    \resumeItemListEnd

  \resumeSubheading
    {Unity Intern}{June 2024 -- Aug 2024}
    {Mindstorm Studios (MLabs) · Lahore}{}
    \resumeItemListStart
      \resumeItem{Built gameplay systems in Unity covering game logic, physics, and asset integration; refined mechanics through repeated playtesting.}
      \resumeItem{Teamed up with three others at \textbf{Summer Rookie Game Jam '24} to design and ship a complete 2D game within a tight deadline.}
    \resumeItemListEnd

  \resumeSubheading
    {Professional Video Editor}{June 2023 -- Present}
    {Upwork.com · Freelance}{}
    \resumeItemListStart
      \resumeItem{Edited client videos on AI topics --- cuts, pacing, captions, colour grading, and motion graphics --- consistently delivered on time with high client satisfaction.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{EmoSense --- AI Emotion Detection} $|$ \emph{Python, YOLOv8, OpenCV, PyTorch, ONNX}}{Jan -- May 2026}
    \resumeItemListStart
      \resumeItem{\textit{Semester AI Project} --- Real-time system that detects faces from a live camera feed and classifies each into one of seven emotions: Angry, Disgust, Fear, Happy, Neutral, Sad, or Surprise.}
      \resumeItem{Two-stage pipeline: face detection model followed by a separately trained emotion classifier, trained on the RAF-DB dataset over 80 rounds; exported to ONNX for faster detection with GPU support.}
      \resumeItem{App displays coloured boxes with emoji badges per face, a confidence slider, live emotion percentage bars, and a dominant emotion readout. Runs on Windows and Linux via a scripted setup system.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{LensCraft --- AI Portrait Mode App} $|$ \emph{C++, Python, OpenCV, rembg, Tkinter, ONNX, PyInstaller}}{2025 -- 2026}
    \resumeItemListStart
      \resumeItem{\textit{OS Course Project} (v1, C++): Co-built a CLI portrait-mode tool using OpenCV's GrabCut for subject isolation and POSIX semaphores to synchronize multithreaded pixel compositing across all available CPU cores.}
      \resumeItem{Ported and extended the project to Python (v2): replaced the CLI with a custom Tkinter GUI featuring an animated splash screen, drag-and-drop image zones, and a side-by-side before/after comparison canvas.}
      \resumeItem{Upgraded segmentation from GrabCut to AI-driven background removal via \texttt{rembg} (U\textsuperscript{2}-Net / ONNX), adding BLUR, GRAY, and TRANS modes; packaged as a standalone Windows executable with PyInstaller.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Origami Configurator} $|$ \emph{Unity, WebGL, C\#, REST APIs}}{2024 -- 2026}
    \resumeItemListStart
      \resumeItem{Designed and built the complete UI/UX, core logic, backend systems, and login APIs for a construction industry product configurator; developed and shipped basic functionality end-to-end across the mobile and browser-based versions.}
      \resumeItem{Browser port supports full 3D model viewing, product configuration, pricing workflows, and core construction tools; original mobile app is live on the Google Play Store.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{2D Slingshot Game} $|$ \emph{C\#, Unity Game Engine, Visual Studio}}{June -- Aug 2024}
    \resumeItemListStart
      \resumeItem{Physics-based slingshot game with projectiles, zombie targets, and destructible obstacles; delivered as a complete Game Jam build.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Snake Game} $|$ \emph{C++, SFML, Visual Studio}}{March -- April 2023}
    \resumeItemListStart
      \resumeItem{Classic Snake remake with smooth controls, custom visuals, and well-structured code; tuned collision and frame logic for responsive gameplay.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages: }{\textit{Python · C / C++ / C\# · SQL · Bash / Shell Scripting}} \\[2pt]
    \textbf{Tools \& Platforms: }{\textit{Git · GitHub · Unity · SFML · Linux · Oracle SQL Developer · Visual Studio · VS Code}} \\[2pt]
    \textbf{AI / ML: }{\textit{YOLOv8 · PyTorch · OpenCV · ONNX · Deep Learning · Scikit-learn}} \\[2pt]
    \textbf{Databases: }{\textit{Oracle SQL · MongoDB}} \hspace{10pt}
    \textbf{Other: }{\textit{Video Editing (Premiere Pro, CapCut) · WebGL}}
  }}
\end{itemize}

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{English: }{\textit{Professional Proficiency}} \hspace{10pt}
    \textbf{Urdu: }{\textit{Native}} \hspace{10pt}
    \textbf{Pashto: }{\textit{Native}}
  }}
\end{itemize}

\end{document}